The SMT Competition 2015--2018

### 2018-11-25 2018/report/SMT-COMP.tex
Minor

\jsatheading{1}{2004}{25-30}
\ShortHeadings{The SMT Competition 2015--2018}
{Weber et al.}
\firstpageno{25}

@@

\published{September 2004}{October 2004}{November 2004}

@@

All solvers are run with four cores available, and the time limit~$T$
that is imposed on each job pair (see Table~\ref{table:time-limits})
is a wall-clock limit.  Thus, solvers that take advantage of
parallelism might use up to~$4T$ CPU time.  For the main track and the
unsat-core track, the competition reports sequential and parallel
performance separately.  The former is determined by imposing a
(virtual) CPU time limit of~$T$.  For the application track,
sequential performance is not recorded (because response times to
individual {\tt check-sat} commands are not available).

>>>>

\jsatheading{1}{2004}{1-25}
\ShortHeadings{The SMT Competition 2015--2018}
{Weber et al.}
\firstpageno{1}

@@

\published{November 2018}{November 2018}{November 2018}

@@

All solvers are run with four cores available, and the time limit~$T$
that is imposed on each job pair (see Table~\ref{table:time-limits})
is a wall-clock limit.  Thus, solvers that take advantage of
parallelism might use up to~$4T$ CPU time.  For the main track and the
unsat-core track, the competition reports parallel and sequential
performance separately.  The latter is determined by imposing a
(virtual) CPU time limit of~$T$.  For the application track, only
parallel performance is reported (because response times to individual
{\tt check-sat} commands are not recorded by StarExec).
